A multi-species benchmark for training and validating large scale mass spectrometry proteomics machine learning models

### 2024-07-24 doc/nine-species/nine-species.tex
Edits
Various minor updates

\begin{figure}
  \centering
  \begin{tabular}{lll}
    \includegraphics[height=1.4in]{nine-species-fdr.pdf} &
    \includegraphics[height=1.4in]{percent-id.pdf}  &
    \includegraphics[height=1.4in]{match-by.pdf}  \\
    a & b & c \\
  \end{tabular}
  \caption{\textbf{Validation of the benchmarks.}
    \textbf{a.} Each series indicates, for a given species, the number of accepted PSMs as a function of PSM-level FDR.
    \textbf{b.} The bar plot indicates the proportion of spectra that were accepted at 1\% PSM-level FDR per species.
    \textbf{c.} Each histogram show the distribution, per species, of the proportion of total ion current that is explained per accepted PSM, using a matching tolerance of 0.05~\textit{m/z}.}
  \label{fig:fdr}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{tabular}{lll}
    \includegraphics[height=4in]{../../results/wnoble/2024-07-17validations/nine-species-fdrs.pdf} &
    \includegraphics[height=4in]{../../results/wnoble/2024-07-17validations/percent-id.pdf}  &
    \includegraphics[height=4in]{../../results/wnoble/2024-07-17validations/match-by.pdf}  \\
    a & b & c \\
  \end{tabular}
  \caption{\textbf{Validation of the benchmarks.}
    \textbf{a.} Each series indicates, for a given species, the number of accepted PSMs as a function of PSM-level FDR.
    \textbf{b.} The bar plot indicates the proportion of spectra that were accepted at 1\% PSM-level FDR per species.
    \textbf{c.} Each histogram shows, for one species, the distribution of the proportion of total ion current that is matched by b- or y-ions per accepted PSM, using a matching tolerance of 0.05~\textit{m/z}.}
  \label{fig:fdr}
\end{figure}
